---
title: "Machine Learning Application Example"
author: "Liliana"
date: "November, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Description
This project shows a "xxx" applycation problem. 

## Data Source
- Age-adjusted Death Rates for Selected Major Causes of Death in the US
- Data is available  at  
<https://data.cdc.gov/api/views/bi63-dtpu/rows.csv?accessType=DOWNLOAD>

## Graphs
- Top 4 States for Alzheimer's Disease
- Top 4 States for Heart Disease

## To see other graphs, go to my Shiny app at the following link
<https://lgaccount.shinyapps.io/shiny_dataproducts_lg/>

Alzheimers Disease: States With The Highest Death Counts and Death Rates 

```{r quiz,echo=FALSE, message=FALSE, warning=FALSE}
library(doBy) #Summaryby
library(ggplot2)
library(caret)
library(spectral)
library (plyr)
library(dplyr)
library(stringr)
library(gridExtra)
#
#inputGiven <<- read.csv('https://data.cdc.gov/api/views/bi63-dtpu/rows.csv?accessType=DOWNLOAD', header=TRUE, sep=",")
inputSubData<-read.csv('https://data.cdc.gov/api/views/bi63-dtpu/rows.csv?accessType=DOWNLOAD', header=TRUE, sep=",")
inputSubData <- subset(inputSubData,select=-c(X113.Cause.Name)) #  removing uneeded columns

```

## Exploratory

You can also embed plots, for example:

```{r exploratory, echo=FALSE}

   # TopStatesNumber <- input$StatesNumber
    #SelectedCause <- input$CauseName
    TopStatesNumber <- 5
    SelectedCause <- "Alzheimer's disease"
    
    
    if(!is.null(SelectedCause)){
      T_Data <- subset(inputSubData, inputSubData$Cause.Name == SelectedCause  & inputSubData$State != "United States")
    }
    
    
    #SelectedState <- input$State1
    SelectedState <- "Illinois"
 
    
    #Selecting top Deaths states only
    T_Data$Deaths <-as.numeric(T_Data$Deaths)
    T_Data_Sum<-aggregate(T_Data$Deaths, list(T_Data$State,T_Data$Cause.Name), sum, na.rm=TRUE) # 
    colnames(T_Data_Sum)<-c("State", "Cause.Name", "Total_Deaths")
    T_Data_Sum <-T_Data_Sum[order(T_Data_Sum$Total_Deaths, decreasing = TRUE),]
    T_Data_Sum <-T_Data_Sum[1:TopStatesNumber,]
    T_Data_Top_D<-subset(T_Data,State==T_Data_Sum$State)
    T_Data_State <-subset(T_Data,State==SelectedState)
    T_Data_Top_D<-rbind(T_Data_Top_D,T_Data_State )

    
    #Selecting Top Death Rate states only
    T_Data$Age.adjusted.Death.Rate <-as.numeric(T_Data$Age.adjusted.Death.Rate)
    T_Data_Sum_DR<-aggregate(T_Data$Age.adjusted.Death.Rate, list(T_Data$State,T_Data$Cause.Name), sum, na.rm=TRUE) # 
    #print(T_Data_Sum_DR)
    colnames(T_Data_Sum_DR)<-c("State", "Cause.Name", "Total_DR")
    T_Data_Sum_DR <-T_Data_Sum_DR[order(T_Data_Sum_DR$Total_DR, decreasing = TRUE),]
    T_Data_Sum_DR <-T_Data_Sum_DR[1:TopStatesNumber,]
    T_Data_Top_DR<-subset(T_Data,State==T_Data_Sum_DR$State)
    T_Data_Top_DR<-rbind(T_Data_Top_DR,T_Data_State )
    
    #
    pt1<- ggplot(T_Data_Top_D, aes(x=Year, y=as.numeric(Deaths),color = State, group = State)) + #linetype = Type, 
    geom_line(size = 1.5) +
    labs(title = paste("Historical Death Records from:  ",SelectedCause  , ",  Comparing the State of: ", SelectedState, "with Top-",TopStatesNumber, " States"), x="Year", y="Deaths count")+
      theme_bw() + 
      theme(#axis.line=element_blank(),panel.background=element_blank(),# panel.border=element_blank(), panel.grid.major=element_blank(),
            #panel.grid.minor=element_blank(),plot.background=element_blank(),
            axis.text.x = element_text(size=12, angle = 90, vjust = 1, color = "black", face = "bold"), axis.text.y = element_text(size=12, color = "black", face = "bold"),
            axis.title = element_text(size = 16, face = "bold"),
            plot.title = element_text(size = 16, face = "bold"),
            strip.text = element_text(size = 16, face = "bold")) #+ #scale_x_date() , ,legend.position="none"
    
    pt2<- ggplot(T_Data_Top_DR, aes(x=Year, y=as.numeric(Age.adjusted.Death.Rate),color = State, group = State)) + #linetype = Type, 
      geom_line(size = 1.5) +
      labs(title = paste("Age-Adjusted Historical Death Rate (deaths per 100,000) from:  ",SelectedCause  , ",  Comparing the State of: ", SelectedState, "with Top-",TopStatesNumber, " States"), x="Year", y="Death Rate")+
      theme_bw() + 
      theme(#panel.background=element_blank(), #panel.border=element_blank(), panel.grid.major=element_blank(),axis.line=element_blank(),plot.background=element_blank(),
            #panel.grid.minor=element_blank(),
            axis.text.x = element_text(size=12, angle = 90, vjust = 1, color = "black", face = "bold"), axis.text.y = element_text(size=12, color = "black", face = "bold"),
            axis.title = element_text(size = 16, face = "bold"),
            plot.title = element_text(size = 16, face = "bold"),
            strip.text = element_text(size = 16, face = "bold")) #+ #scale_x_date() , ,legend.position="none"
     
     grid.arrange(pt1,pt2)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
